Higher-Order unification for free!

### 2024-07-01 paper/main.tex
line 1324; "since it removes all THE data from THE rule's heads"

\noindent
where \elpiIn{unify} is a regular predicate.
This method fails to take advantage of the logic
programming engine provided by the meta language since
it removes all data from rule's heads and makes
indexing degrade. Additionally,
implementing a unification procedure in the meta language is likely to be significantly
slower compared to the built-in one on the common domain of first order terms.

>>>>

\noindent
where \elpiIn{unify} is a regular predicate.
This method fails to take advantage of the logic
programming engine provided by the meta language since
it removes all the data from the rule's heads and makes
indexing degrade. Additionally,
implementing a unification procedure in the meta language is likely to be significantly
slower compared to the built-in one on the common domain of first order terms.
